Estimating the Performance of Entity Resolution Algorithms: Lessons Learned Through PatentsView.org

### 2022-09-21 paper/main.tex
update paper

\title{Estimating the Performance of Entity Resolution Algorithms: New Approach and a Case Study at PatentsView.org}

@@

\begin{table}\label{tab:precision_results}
    \centering
    \caption{\centering Bias and root mean squared error (rmse) of precision estimators for the simulation study described in section \ref{sec:simulation_study}. The \texttt{rate} variable represents the percentage misattribution rate.}
\begin{tabular}{llccccccccc}
\toprule
{} & \hfill{\textbf{rate}} & \multicolumn{3}{c}{5} & \multicolumn{3}{c}{10} & \multicolumn{3}{c}{20} \\
\cmidrule(lr){3-5}\cmidrule(lr){6-8}\cmidrule(lr){9-11}
{} & \hfill{\textbf{sample size}} & {100} & {200} & {400} & {100} & {200} & {400} & {100} & {200} & {400} \\
\midrule
\multirow[c]{4}{*}{\textbf{bias}} & P\_cluster\_block & -0.004 & -0.002 & -0.001 & -0.002 & -0.001 & 0.001 & -0.004 & -0.001 & -0.000 \\
 & P\_naive & 0.099 & 0.099 & 0.099 & 0.195 & 0.195 & 0.195 & 0.366 & 0.366 & 0.365 \\
 & P\_record & -0.002 & 0.013 & 0.009 & -0.001 & 0.011 & 0.008 & -0.001 & 0.009 & 0.006 \\
\midrule
\multirow[c]{4}{*}{\textbf{rmse}} & P\_cluster\_block & 0.045 & 0.033 & 0.021 & 0.041 & 0.038 & 0.026 & 0.063 & 0.052 & 0.034 \\
 & P\_naive & 0.099 & 0.099 & 0.099 & 0.195 & 0.195 & 0.195 & 0.366 & 0.366 & 0.365 \\
 & P\_record & 0.294 & 0.232 & 0.169 & 0.260 & 0.205 & 0.150 & 0.207 & 0.162 & 0.117 \\
\bottomrule
\end{tabular}
\end{table}

@@

\begin{table}\label{tab:recall_results}
    \centering
    \caption{\centering Bias and root mean squared error of recall estimators for the simulation study described in section \ref{sec:simulation_study}. The \texttt{rate} variable represents the percentage misattribution rate.}
\begin{tabular}{llccccccccc}
\toprule
{} & {\textbf{rate}} & \multicolumn{3}{c}{{5}} & \multicolumn{3}{c}{10} & \multicolumn{3}{c}{20} \\
\cmidrule(lr){3-5}\cmidrule(lr){6-8}\cmidrule(lr){9-11}
{} & {\textbf{sample size}} & {100} & {200} & {400} & {100} & {200} & {400} & {100} & {200} & {400} \\
\midrule
\multirow[c]{2}{*}{\textbf{bias}} & R\_naive & 0.0007 & 0.0001 & 0.0004 & 0.0009 & -0.0015 & -0.0024 & -0.0008 & -0.0010 & -0.0017 \\
 & R\_record & 0.0002 & -0.0001 & -0.0002 & 0.0011 & -0.0002 & -0.0004 & 0.0005 & 0.0001 & -0.0002 \\
 \midrule
\multirow[c]{2}{*}{\textbf{rmse}} & R\_naive & 0.0089 & 0.0056 & 0.0043 & 0.0123 & 0.0089 & 0.0075 & 0.0132 & 0.0109 & 0.0091 \\
 & R\_record & 0.0060 & 0.0037 & 0.0028 & 0.0089 & 0.0056 & 0.0039 & 0.0099 & 0.0071 & 0.0050 \\
\bottomrule
\end{tabular}

@@

\begin{proof}[Proof of lemma \ref{lemma:record_sampling_representation}]
By breaking down $\mathcal{P}$ and $\mathcal{T}$ over predicted clusters, we find
\begin{equation}
    P = \sum_{c\in\mathcal{C}} \sum_{\hat c \in \widehat{\mathcal{C}}} {\lvert c \cap \hat c \rvert \choose 2} \Big/ \sum_{\hat c \in \widehat{\mathcal{C}}} {\lvert \hat c \rvert \choose 2}.
\end{equation}
Now writing $\sum_{c \in \mathcal{C}} \sum_{\hat c \in \widehat{\mathcal{C}}}{\lvert c \cap \hat c \rvert \choose 2} = \sum_{i=1}^{N} \frac{1}{\lvert c(i) \rvert} \sum_{\hat c \in \widehat{\mathcal{C}}} {\lvert c(i) \cap \hat c \rvert \choose 2}$ and substituting $g(c(i), \widehat{\mathcal{C}})$, we obtain
\begin{equation}
    P = \sum_{i=1}^N p_i \frac{g(c(i)), \widehat{\mathcal{C}})}{p_i \lvert c(i) \rvert} = \mathbb{E}\left[ \frac{g(c(i)), \widehat{\mathcal{C}}}{p_i \lvert c(i) \rvert} \right].
\end{equation}
For recall, write 
\begin{equation}\label{eq:recall_cluster_form}
    R = \sum_{c\in\mathcal{C}} \sum_{\hat c \in \widehat{\mathcal{C}}} {\lvert c \cap \hat c \rvert \choose 2} \Big/ \sum_{ c \in {\mathcal{C}}} {\lvert c \rvert \choose 2}.
\end{equation}
Through a similar argument as above, we may express the numerator as 
\begin{equation}\label{eq:nominator}
    \sum_{c\in\mathcal{C}} \sum_{\hat c \in \widehat{\mathcal{C}}} {\lvert c \cap \hat c \rvert \choose 2} = \mathbb{E}\left[ f(c(i),\, \widehat{\mathcal{C}})  \big/ (\lvert c(i) \rvert p_i) \right].
\end{equation}
For the denominator, we have
\begin{equation}\label{eq:denominator}
    \sum_{c \in \mathcal{C}} {\lvert c \rvert \choose 2} = \sum_{i=1}^N \frac{1}{\lvert c(i) \rvert}  {\lvert c(i) \rvert \choose 2} = \mathbb{E}[ (\lvert c(i) \rvert - 1)/(2 p_i)].
\end{equation}
Combining \eqref{eq:nominator} and \eqref{eq:denominator} yields the result. 
\end{proof}

>>>>

\title{Estimating the Performance of Entity Resolution Algorithms: Lessons Learned Through PatentsView.org}
%\title{Estimating the Performance of Entity Resolution Algorithms: New Approach and a Case Study for PatentsView.org}

@@

\begin{table}
    \centering
    \caption{\label{tab:precision_results}\centering Bias and root mean squared error (rmse) of precision estimators for the simulation study described in section \ref{sec:simulation_study}. The \texttt{rate} variable represents the percentage misattribution rate.}
\begin{tabular}{llccccccccc}
\toprule
{} & \hfill{\textbf{rate}} & \multicolumn{3}{c}{5} & \multicolumn{3}{c}{10} & \multicolumn{3}{c}{20} \\
\cmidrule(lr){3-5}\cmidrule(lr){6-8}\cmidrule(lr){9-11}
{} & \hfill{\textbf{sample size}} & {100} & {200} & {400} & {100} & {200} & {400} & {100} & {200} & {400} \\
\midrule
\multirow[c]{4}{*}{\textbf{bias}} & P\_cluster\_block & -0.004 & -0.002 & -0.001 & -0.002 & -0.001 & 0.001 & -0.004 & -0.001 & -0.000 \\
 & P\_naive & 0.099 & 0.099 & 0.099 & 0.195 & 0.195 & 0.195 & 0.366 & 0.366 & 0.365 \\
 & P\_record & -0.002 & 0.013 & 0.009 & -0.001 & 0.011 & 0.008 & -0.001 & 0.009 & 0.006 \\
\midrule
\multirow[c]{4}{*}{\textbf{rmse}} & P\_cluster\_block & 0.045 & 0.033 & 0.021 & 0.041 & 0.038 & 0.026 & 0.063 & 0.052 & 0.034 \\
 & P\_naive & 0.099 & 0.099 & 0.099 & 0.195 & 0.195 & 0.195 & 0.366 & 0.366 & 0.365 \\
 & P\_record & 0.294 & 0.232 & 0.169 & 0.260 & 0.205 & 0.150 & 0.207 & 0.162 & 0.117 \\
\bottomrule
\end{tabular}
\end{table}

@@

\begin{table}
    \centering
    \caption{\label{tab:recall_results}\centering Bias and root mean squared error of recall estimators for the simulation study described in section \ref{sec:simulation_study}. The \texttt{rate} variable represents the percentage misattribution rate.}
\begin{tabular}{llccccccccc}
\toprule
{} & {\textbf{rate}} & \multicolumn{3}{c}{{5}} & \multicolumn{3}{c}{10} & \multicolumn{3}{c}{20} \\
\cmidrule(lr){3-5}\cmidrule(lr){6-8}\cmidrule(lr){9-11}
{} & {\textbf{sample size}} & {100} & {200} & {400} & {100} & {200} & {400} & {100} & {200} & {400} \\
\midrule
\multirow[c]{2}{*}{\textbf{bias}} & R\_naive & 0.0007 & 0.0001 & 0.0004 & 0.0009 & -0.0015 & -0.0024 & -0.0008 & -0.0010 & -0.0017 \\
 & R\_record & 0.0002 & -0.0001 & -0.0002 & 0.0011 & -0.0002 & -0.0004 & 0.0005 & 0.0001 & -0.0002 \\
 \midrule
\multirow[c]{2}{*}{\textbf{rmse}} & R\_naive & 0.0089 & 0.0056 & 0.0043 & 0.0123 & 0.0089 & 0.0075 & 0.0132 & 0.0109 & 0.0091 \\
 & R\_record & 0.0060 & 0.0037 & 0.0028 & 0.0089 & 0.0056 & 0.0039 & 0.0099 & 0.0071 & 0.0050 \\
\bottomrule
\end{tabular}

@@

\begin{proof}[Proof of lemma \ref{lemma:record_sampling_representation}]
By breaking down $\mathcal{P}$ and $\mathcal{T}$ over predicted clusters, we find
\begin{equation}
    P = \sum_{c\in\mathcal{C}} \sum_{\hat c \in \widehat{\mathcal{C}}} {\lvert c \cap \hat c \rvert \choose 2} \Big/ \sum_{\hat c \in \widehat{\mathcal{C}}} {\lvert \hat c \rvert \choose 2}.
\end{equation}
Now writing $\sum_{c \in \mathcal{C}} \sum_{\hat c \in \widehat{\mathcal{C}}}{\lvert c \cap \hat c \rvert \choose 2} = \sum_{i=1}^{N} \frac{1}{\lvert c(i) \rvert} \sum_{\hat c \in \widehat{\mathcal{C}}} {\lvert c(i) \cap \hat c \rvert \choose 2}$ and substituting $g(c(i), \widehat{\mathcal{C}})$, we obtain
\begin{equation}
    P = \sum_{i=1}^N p_i \frac{g(c(i)), \widehat{\mathcal{C}})}{p_i \lvert c(i) \rvert} = \mathbb{E}\left[ \frac{g(c(i), \widehat{\mathcal{C}})}{p_i \lvert c(i) \rvert} \right].
\end{equation}
For recall, write 
\begin{equation}\label{eq:recall_cluster_form}
    R = \sum_{c\in\mathcal{C}} \sum_{\hat c \in \widehat{\mathcal{C}}} {\lvert c \cap \hat c \rvert \choose 2} \Big/ \sum_{ c \in {\mathcal{C}}} {\lvert c \rvert \choose 2}.
\end{equation}
Through a similar argument as above, we may express the numerator as 
\begin{equation}\label{eq:nominator}
    \sum_{c\in\mathcal{C}} \sum_{\hat c \in \widehat{\mathcal{C}}} {\lvert c \cap \hat c \rvert \choose 2} = \mathbb{E}\left[ f(c(i),\, \widehat{\mathcal{C}})  \big/ (\lvert c(i) \rvert p_i) \right].
\end{equation}
For the denominator, we have
\begin{equation}\label{eq:denominator}
    \sum_{c \in \mathcal{C}} {\lvert c \rvert \choose 2} = \sum_{i=1}^N \frac{1}{\lvert c(i) \rvert}  {\lvert c(i) \rvert \choose 2} = \mathbb{E}[ (\lvert c(i) \rvert - 1)/(2 p_i)].
\end{equation}
Combining \eqref{eq:nominator} and \eqref{eq:denominator} yields the result. 
\end{proof}
